---
title: "Mapping Shark Research"
author: "Rémi Toupin and Philippe Mongeon"
date: "2020-12-07"
abstract: "This is an abstract"
output: 
  html_document:
    toc: true 
    toc_float:       
      collapsed: false
    toc_depth: 2
    number_sections: false 
    theme: lumen
    highlight: tango
#    css: my.css   # you can add your custom css, should be in same folder
# Themes: "cerulean", "journal", "flatly", "darkly", "readable", "spacelab", "united", "cosmo", "lumen", "paper", "sandstone", "simplex", "yeti"
# Highlights: "tango", "pygments", "kate", "monochrome", "espresso", "zenburn", "haddock", "breezedark", "textmate"

---

# Summary

# Collecting the publications

We collect all publications containing the term “shark” and published between 1980 and 2020 from the Web of 
Science (WoS) database hosted by the Centre for Science and Technology Studies (CWTS) using the following SQL code:

```{sql eval=FALSE}
SELECT DISTINCT ut INTO #data from wos_2013_text..text_data where CONTAINS(title, 'shark')
union select ut from wos_2013_text..text_data where CONTAINS(title, 'sharks') 
union select ut from wos_2013_text..text_data where CONTAINS(keyword, 'shark')
union select ut from wos_2013_text..text_data where CONTAINS(keyword, 'sharks')
union select ut from wos_2013_text..text_data where CONTAINS(keyword_plus, 'shark')
UNION select ut from wos_2013_text..text_data where CONTAINS(keyword_plus, 'sharks')
UNION select ut from wos_2013_text..text_data where CONTAINS(abstract, 'shark')
UNION SELECT ut from wos_2013_text..text_data WHERE CONTAINS(abstract, 'sharks')
```

# Building the network 

```{r eval=FALSE}
# Load needed packages
library(tidyverse)
library(igraph)

# Load data

Articles <- read_delim(unzip("data/articles.zip"), delim="\t")
Citations <- read_delim(unzip("data/citations.zip"), delim="\t")

# bibliographic coupling network
BCNetwork <- select(Articles, ut) %>% 
  inner_join(Citations, by=c("ut" = "citing_ut")) %>% 
  inner_join(Citations, by="cited_ut") %>% 
  inner_join(select(Articles,ut), by=c("citing_ut" = "ut")) %>% 
  select(source = ut, target = citing_ut) %>%
  filter(target > source) %>% 
  count(source, target, name = "weight") %>% 
  mutate(type = "undirected")
  
# co-citation network
CCNetwork <- select(Articles, ut) %>% 
  inner_join(Citations, by=c("ut" = "cited_ut")) %>% 
  inner_join(Citations, by="citing_ut") %>% 
  inner_join(select(Articles,ut), by=c("cited_ut" = "ut")) %>% 
  select(source = ut, target = cited_ut) %>%
  filter(target > source) %>% 
  count(source, target, name = "weight") %>% 
  mutate(type = "undirected")

# Combined BC+CC network
CCBCNetwork <- rbind(CCNetwork,BCNetwork) %>%
  group_by(source, target, type) %>% 
  summarize(weight = sum(weight)) %>% 
  ungroup()

# Remove objects that are no longer needed
remove(CCNetwork, BCNetwork)
```

# Identifying the communities

### macro-clusters

```{r eval=FALSE}
# create igraph object
network <- graph_from_data_frame(CCBCNetwork, directed = F) %>% simplify(remove.loops = TRUE)

#keep only the main component
V(network)$comp <- components(network)$membership
network <- induced_subgraph(network, V(network)$comp==1)

# Identify communities
V(network)$community <- cluster_louvain(network, weights = c(E(network)$Weight))$membership

# Add macro cluster to the articles table
Articles <- Articles %>% 
  left_join(select(as_data_frame(network, "both")$vertices, name, macro_cluster = community), by=c("ut" = "name"))
            
```

### meso-clusters

```{r eval=FALSE}

j = 0
for (i in 1:max(filter(Articles, !is.na(macro_cluster))$macro_cluster)) {

# create igraph object

network <- CCBCNetwork %>% 
  inner_join(select(filter(Articles, macro_cluster == i),ut), by=c("source" = "ut")) %>% 
  inner_join(select(filter(Articles, macro_cluster == i),ut), by=c("target" = "ut")) %>% 
  graph_from_data_frame(directed = F) %>% 
  simplify(remove.loops = TRUE)

#keep only the main component
V(network)$comp <- components(network)$membership
network <- induced_subgraph(network, V(network)$comp==1)

# Identify communities
V(network)$community <- cluster_louvain(network, weights = c(E(network)$Weight))$membership

# List of articles with their community
if (i==1){
x <-  select(as_data_frame(network, "both")$vertices, name, meso_cluster = community) %>% 
  mutate(meso_cluster = meso_cluster+j)
meso_cluster <- select(Articles,ut) %>% 
  inner_join(x, by=c("ut" = "name"))
}
if (i>1){
x <-  select(as_data_frame(network, "both")$vertices, name, meso_cluster = community) %>% 
  mutate(meso_cluster = meso_cluster+j)
meso_cluster <- rbind(meso_cluster, select(Articles,ut) %>% 
  inner_join(x, by=c("ut" = "name")))
}
j = max(meso_cluster$meso_cluster)
}

# Add meso clusters to Articles

Articles <- Articles %>% 
  left_join(meso_cluster, by="ut")

```

### micro-clusters

```{r eval=FALSE}

j=0
for (i in 1:max(filter(Articles, !is.na(meso_cluster))$meso_cluster)) {
# create igraph object

network <- CCBCNetwork %>% 
  inner_join(select(filter(Articles, meso_cluster == i),ut), by=c("source" = "ut")) %>% 
  inner_join(select(filter(Articles, meso_cluster == i),ut), by=c("target" = "ut")) %>% 
  graph_from_data_frame(directed = F) %>% 
  simplify(remove.loops = TRUE)

#keep only the main component
V(network)$comp <- components(network)$membership
network <- induced_subgraph(network, V(network)$comp==1)

# Identify communities
V(network)$community <- cluster_louvain(network, weights = c(E(network)$Weight))$membership

# List of articles with their community
if (i==1){
x <-  select(as_data_frame(network, "both")$vertices, name, micro_cluster = community) %>% 
  mutate(micro_cluster = micro_cluster+j)

micro_cluster <- select(Articles,ut) %>% 
  inner_join(x, by=c("ut" = "name"))
}
if (i>1){
x <-  select(as_data_frame(network, "both")$vertices, name, micro_cluster = community) %>% 
  mutate(micro_cluster = micro_cluster+j)
micro_cluster <- rbind(micro_cluster, select(Articles,ut) %>% 
  inner_join(x, by=c("ut" = "name")))
}
j = max(micro_cluster$micro_cluster)
}

Articles <- Articles %>% 
  left_join(micro_cluster, by="ut")

# export articles

write_delim(Articles, "data/articles_clusters.txt", delim="\t")
```

# Characterizing the communities

```{r eval = FALSE}

##=================
#create summary table of topics by community
#gamma is the fitting coefficient of a document to a topic
#IMPORTANT : check for weighted measures of topic to community
##=================
summarynodes <- df$vertices %>%
  group_by(community) %>%
  summarise(npapers = n_distinct(name),
            ntopic = n_distinct(topic, na.rm = T),
            most_topic = pracma::Mode(topic),
            most_topic_median = median(gamma, na.rm = TRUE),
            gamma1 = median(gamma1[gamma1>=0.1], na.rm= T),
            gamma2 = median(gamma2[gamma2>=0.1], na.rm= T),
            gamma3 = median(gamma3[gamma3>=0.1], na.rm= T),
            gamma4 = median(gamma4[gamma4>=0.1], na.rm= T),
            gamma5 = median(gamma5[gamma5>=0.1], na.rm= T),
            gamma6 = median(gamma6[gamma6>=0.1], na.rm= T),
            gamma7 = median(gamma7[gamma7>=0.1], na.rm= T),
            gamma8 = median(gamma8[gamma8>=0.1], na.rm= T),
            gamma9 = median(gamma9[gamma9>=0.1], na.rm= T),
            gamma10 = median(gamma10[gamma10>=0.1], na.rm= T),
            gamma11 = median(gamma11[gamma11>=0.1], na.rm= T),
            gamma12 = median(gamma12[gamma12>=0.1], na.rm= T),
            gamma13 = median(gamma13[gamma13>=0.1], na.rm= T),
            gamma14 = median(gamma14[gamma14>=0.1], na.rm= T),
            gamma15 = median(gamma15[gamma15>=0.1], na.rm= T),
            gamma16 = median(gamma16[gamma16>=0.1], na.rm= T),
            gamma17 = median(gamma17[gamma17>=0.1], na.rm= T),
            gamma18 = median(gamma18[gamma18>=0.1], na.rm= T),
            gamma19 = median(gamma19[gamma19>=0.1], na.rm= T),
            )

write_csv(df$edges, "BC_Louvain_edges.csv")
write_csv(df$vertices, "BC_Louvain_vertices.csv")
write_csv(summarynodes, "BC_Louvain_vertices_summary.csv")

df$vertices %>%
  count(topic)

```

# Visualizing the communities

```{r eval=FALSE}
head(CCBCNetwork)

macro_network <- CCBCNetwork %>% 
  inner_join(select(Articles, ut, macro_cluster), by=c("source" = "ut"))%>%
  inner_join(select(Articles, ut, macro_cluster), by=c("target" = "ut")) %>% 
  select(source = macro_cluster.x, target = macro_cluster.y, weight, type) %>%
  filter(target > source) %>% 
  group_by(source, target, type) %>% 
  summarize(weight = sum(weight))

meso_network <- CCBCNetwork %>% 
  inner_join(select(Articles, ut, meso_cluster), by=c("source" = "ut"))%>%
  inner_join(select(Articles, ut, meso_cluster), by=c("target" = "ut")) %>% 
  select(source = meso_cluster.x, target = meso_cluster.y, weight, type) %>%
  filter(target > source) %>% 
  group_by(source, target, type) %>% 
  summarize(weight = sum(weight))

micro_network <- CCBCNetwork %>% 
  inner_join(select(Articles, ut, micro_cluster), by=c("source" = "ut"))%>%
  inner_join(select(Articles, ut, micro_cluster), by=c("target" = "ut")) %>% 
  select(source = micro_cluster.x, target = micro_cluster.y, weight, type) %>%
  filter(target > source) %>% 
  group_by(source, target, type) %>% 
  summarize(weight = sum(weight))


library("visNetwork")
graph <- graph_from_data_frame(meso_network, directed = FALSE)

visIgraph(graph)

```



